\documentclass{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{accents}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsthm}
\usepackage{soul}
\usepackage[margin=15mm]{geometry}
\usepackage[makeroom]{cancel}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\hypersetup{colorlinks=true,linkcolor=blue, linktocpage}
% Set up fancy header
\pagestyle{fancy}
\fancyhf{} % Clear default header and footer
\rhead{Keith Wesa} % Right header
\lhead{CS 151 Homework 2:} % Left header
\rfoot{Page \thepage} % Right footer

\author{Keith Wesa}
\title{MAT 215 - Written Homework 1}
\date{\today}

\begin{document}
\section*{Question 3}
\subsection*{The problem}
\begin{itemize}
    \item[Q3] Prove that for any integer $n$, $n$ is odd if and only if $5n +3$ is even.
    Indicate which proof methods you used, as well as the assumptions (what you suppose)
    and the conclusions (what you need to show) of the proof.
    \item[] \textbf{Logical statement:} $\forall n \in \mathbb{Z}, n \text{ is odd} \Leftrightarrow 5n + 3 \text{ is even}$
    \item[] \textbf{Simplify Variables:} Let $n = N(x))$ and $5n + 3 = E(y)$ $x, y \in \mathbb{Z} x=2k, y = 2k+1$ for some $k \in \mathbb{Z}$ 
    \item[] \textbf{Rewrite the statement:} $\forall x, y \in \mathbb{Z} N(y) \Leftrightarrow E(x)$
    \item[] \textbf{Define: } Even: $x = 2n$ for some $n \in \mathbb{Z}$
    \item[] \textbf{Define: } Odd: $x = 2n + 1$ for some $n \in \mathbb{Z}$
    \item[] \textbf{Thoughts on the problem: } We can prove this problem by contradiction. We can assume that $n$ is odd and $5n + 3$ is odd
    \item[] \textbf{Contradiction:} $\lnot p \land \lnot q$ which is
    \begin{equation*}
        \begin{aligned}
            &\lnot(\forall x, y \in \mathbb{Z} N(y) \Leftrightarrow E(x)) \\
            &\lnot(\forall x, y \in \mathbb{Z} (N(y) \Rightarrow E(x)) \land (E(x) \Rightarrow N(y))) \\
            &\lnot(\forall x, y \in \mathbb{Z} (\lnot N(y) \lor E(x)) \land (\lnot E(x) \lor N(y))) \\
            &\exists x, y \in \mathbb{Z} \lnot (\lnot N(y) \lor E(x)) \lor \lnot (\lnot E(x) \lor N(y)) \\
            &\exists x, y \in \mathbb{Z} (N(y) \land \lnot E(x)) \lor (E(x) \land \lnot N(y)) \\
        \end{aligned}
    \end{equation*}
    \item[] \textbf{More thoughts on the problem: } I'm going to need to do two cases for the proof by contradiction one for $n$ being odd and $5n + 3$ being even and the other for $n$ being even and $5n + 3$ being odd.
    I will have to show that both cases lead to a contradiction because they are tied together by an "OR" statement.
\end{itemize}
\subsection*{Proof by Contradiction}
\begin{proof}
    \begin{itemize}
    \item[] \textbf{Hypothesis: } For any integer $n$, $n$ is odd if and only if $5n + 3$ is even.
    \item[] \textbf{Contradiction:} There exists an integer $n$ such that $n$ is odd and $5n + 3$ is odd or there exists an integer $n$ such that $n$ is even and $5n + 3$ is even.
    \item[] \textbf{Define Set: }$n, k, l \in \mathbb{Z}$
    \item[]
    \item[] \textbf{Case 1:} $n$ is odd and $5n + 3$ is odd
        \begin{align*}
        n &= 2k + 1 \\
        5n + 3 &= 2l + 1 \\
        5(2k + 1) + 3 &= 2l + 1 \\
        10k + 5 + 3 &= 2l + 1 \\
        10k + 8 &= 2l + 1 \\
        10k + 7 &= 2l \\
        \end{align*}
        \item[] This is a contradiction because $10k + 7$ is odd and $2l$ is even.
    \item[] \textbf{Case 2:} $n$ is even and $5n + 3$ is even
        \begin{align*}
        n &= 2k \\
        5n + 3 &= 2l \\
        5(2k) + 3 &= 2l \\
        10k + 3 &= 2l
        \end{align*}
        \item[] This is a contradiction because $10k + 3$ is odd and $2l$ is even.
    \item[] \textbf{Conclusion:} The hypothesis is true because both cases lead to a contradiction.
    \item[] Therefore, for any integer $n$, $n$ is odd if and only if $5n + 3$ is even.
    \end{itemize}
\end{proof}

\end{document}