\documentclass{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{accents}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsthm}
\usepackage{soul}
\usepackage[margin=15mm]{geometry}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\hypersetup{colorlinks=true,linkcolor=blue, linktocpage}
% Set up fancy header
\pagestyle{fancy}
\fancyhf{} % Clear default header and footer
\rhead{Keith Wesa} % Right header
\lhead{CS 151 Homework 2:} % Left header
\rfoot{Page \thepage} % Right footer

\author{Keith Wesa}
\title{MAT 215 - Written Homework 1}
\date{\today}

\begin{document}
\section*{Question 2.1}
\subsection*{The problem}
\begin{itemize}
    \item[Q2.1] For any integer $x$, if $x+y > 50$, then $x > 20$ or $y > 30$.
    \item[] \textbf{Compound Logic Form: } $\forall x \in \mathbb{Z}, \forall y \in \mathbb{Z}, x+y > 50 \rightarrow x > 20 \lor y > 30$
    \item[] \textbf{Simplify Variables: } $x+y = p, x = q, y = r$
    \item[] \textbf{Rewrite: } $p \rightarrow q \lor r$
    \item[] \textbf{Thoughts on the problem:} We can do a direct proof or a contrapositive proof. I will do both.
    \item[] \textbf{Contrapositive: } $\neg q \land \neg r \rightarrow \neg p$
\end{itemize}
\subsection*{Proof by Cases}
\begin{proof}
    If $x+y > 50$, then $x > 20$ or $y > 30$.  
    \begin{align*}
        \text{Case 1: } & x \leq 20 \text{ and } y \leq 30 \\
        \text{Let } & x = 20 \text{ and } y = 30 \text{ they are both integers.} \\
        \text{Then } & x+y = 50 \text{ this is True.}\\
        \text{Case 2: } & x \leq 20 \text{ and } y > 30 \\
        \text{Let } & x = 20 \text{ and } y = 31 \text{ they are both integers.} \\
        \text{Then } & x+y = 51 \text{ this is True.}\\
        \text{Case 3: } & x > 20 \text{ and } y \leq 30 \\
        \text{Let } & x = 21 \text{ and } y = 30 \text{ they are both integers.} \\
        \text{Then } & x+y = 51 \text{ this is True.}\\
        \text{Case 4: } & x > 20 \text{ and } y > 30 \\
        \text{Let } & x = 21 \text{ and } y = 31 \text{ they are both integers.} \\
        \text{Then } & x+y = 52 \text{ this is True.}\\
        \end{align*}
    Therefore, since it is true forall cases, the statement is true.
\end{proof}
\subsection*{Proof by Contrapositive}
\begin{proof}
    If $x \leq 20$ and $y \leq 30$, then $x+y \leq 50$.  
    \begin{align*}
        \text{Let } & x = 20 \text{ and } y = 30 \text{ they are both integers.} \\
        \text{Then } & x+y = 50 \text{ this is True.}\\      
        \end{align*}
    Since, the contrapositive is true, the original statement is true. By the law of contrapositive.
\end{proof}
\end{document}