\documentclass{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{accents}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsthm}
\usepackage{soul}
\usepackage[margin=15mm]{geometry}
\usepackage[makeroom]{cancel}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\hypersetup{colorlinks=true,linkcolor=blue, linktocpage}
% Set up fancy header
\pagestyle{fancy}
\fancyhf{} % Clear default header and footer
\rhead{Keith Wesa} % Right header
\lhead{CS 151 Homework 2:} % Left header
\rfoot{Page \thepage} % Right footer

\author{Keith Wesa}
\title{MAT 215 - Written Homework 1}
\date{\today}

\begin{document}
\section*{Question 2.5}
\subsection*{The problem}
\begin{itemize}
    \item[Q2.5] For any integer $x$ and $y$, if $x+y$ is odd, then $x$ and $y$ have opposite parity.
    \item[] \textbf{Define: } Even Number: A number is even if it is divisible by 2, or if it is equal to $2k$ for some integer $k$.
    \item[] \textbf{Define: } Odd Number: A number is odd if it is not even, or if it is equal to $2k + 1$ for some integer $k$.
    \item[] \textbf{Logical Variables:} $ S(x)= x + y = 2k + 1, p = x, q = y$
    \item[] \textbf{Expressed as a Universal Statement:} $\forall x, y \in \mathbb{Z}, S(x) \rightarrow p \land q$
    \item[] \textbf{Thoughts on the problem: } We can prove this problem by contradiction. We can assume that $x + y$ is odd and $x$ and $y$ have the same parity. 
    Then we can show that this assumption leads to a contradiction.
    \item[] \textbf{Contradiction:} $p \land \lnot q$ 
\end{itemize}
\subsection*{Proof by Contradiction}
\begin{proof}
    
    \begin{itemize}
        \item[]Using the definition of an odd number assume that $x + y$ is odd and $x$ and $y$ have the same parity. Then there exists an integer $k$ such that $x + y = 2k + 1$ and there exists an integer $l$ such that $x = 2l$ and $y = 2l$.
        \item[] \textbf{Defining Set: }$x, y, k, l, i \in \mathbb{Z}$
        \begin{align*}
        x + y &= 2k + 1 \\
        x &= 2l \\
        y &= 2l \\
        2l + 2l &= 2k + 1 \\
        4l &= 2k + 1 \\
        2(2l) &= 2k + 1 \\
        i &= 2l \\
        2i &= 2k + 1 \\
        \end{align*}
        \item[] This is a contradiction because $2i$ is even and $2k + 1$ is odd.
        \item[] Therefore, the assumption that $x + y$ is odd and $x$ and $y$ have the same parity is false. Our original statement is true.
    \end{itemize}
\end{proof}
\end{document}